Collective excitations in the 2- and 3-dimensional extended Hubbard model

### 2023-11-29 paper/main.tex
uni

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Abstract text Abstract text Abstract text Abstract text Abstract text Abstract text Abstract text 
\end{abstract}

@@

where $N$ is the number of lattice sites in the system. 
Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.
The first operator catches the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behaviour of the CDW and AFM states, respectively.

@@

Let us first show and discuss the general form of the spectral functions
\begin{equation}
    \mathcal{A}(\omega) = -\frac{1}{\pi} \Im \left[ \mathcal{G}(\omega + i0^+) \right]
\end{equation}

in the SC and CDW phase and afterward, we will describe the behaviour of the occurring modes as the system approaches a phase transition.
\newline
Firstly, all of the operators mentioned in \eqref{eqn:resolvent_bases} are (anti-)Hermitian. 
Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
all spectral functions must be symmetrical about $\omega=0$. 
For this reason, we will only show the $\omega \geq 0$ in our plots.
\newline
The corresponding spectral functions in the SC and CDW phases are shown in \autoref{fig:resolvent_overview_SC}.
We chose $U=-2$ for all plots and $V=\pm0.1$.

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
    The left edge of the plots is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
    The shaded area marks the two-particle continuum.
    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
    \label{fig:resolvent_overview_SC}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  Abstract                                                 %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We investigate the superconducting (SC), charge-density wave (CDW), and antiferromagnetic (AFM) phases 
    in the extended Hubbard model at zero temperature and half-filling.
    We employ the iterated equations of motion approach \cite{Kalthoff17,bleicker18} to compute the two-particle Green's functions and
    by extension, the corresponding spectral densities.
    This renders a comprehensive analysis of the behaviour of collective excitations possible
    as the model's parameters are changed across phase transitions.
    We identify the well-known amplitude (Higgs) and phase (Leggett) modes within the 
    superconducting phase and observe a similar excitation in the CDW phase
    which shift towards zero energy as the system approaches the phase transition to the SC phase.
    In the CDW phase, close to the phase transition to the AFM phase, we find a collective mode 
    which does not change significantly and another modes which becomes soft
    as the phase boundary is approached.
\end{abstract}

@@

where $N$ is the number of lattice sites in the system. 
Note, that this choice of normalization cancels out with other system size-dependent terms so that our final results do not depend on it at all.
The first operator catches the amplitude mode of the $s$-wave superconducting state, while the second one catches the phase mode \cite{Fan22}.
The remaining two capture the collective behaviour of the CDW and AFM states, respectively.
\newline
Note additionally, that all of the aforementioned operators are (anti-)Hermitian. 
Therefore, their commutator $[A^\dagger, A]$ vanishes and, 
abiding by the sum rule $\int_{-\infty}^\infty \mathcal{A}_{A^\dagger A} (\omega) \mathrm{d}\omega = \langle [A^\dagger, A] \rangle = 0$ \cite{rickayzen80},
all spectral functions

\begin{equation}
    \mathcal{A}(\omega) = -\frac{1}{\pi} \Im \left[ \mathcal{G}(\omega + i0^+) \right]
\end{equation}

must be symmetrical about $\omega=0$.
For this reason, we will only show the $\omega \geq 0$ in our plots.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/resolvent_overview_SC_CDW.pdf}
    \caption{Spectral functions with respect to the operators listed in \eqref{eqn:resolvent_bases}.
    The left column shows the results for the square lattice while the right column shows the results for the simple cubic lattice.
    The left edge of each plot is at $-0.05$ rather than $0$ in order to improve the visibility of the phase peak.
    The shaded area marks the two-particle continuum.
    The panels (a), (b), and (c) show the spectral functions in the SC and CDW phases, respectively.}
    \label{fig:resolvent_overview_SC}
\end{figure*}

Let us first show and discuss the general form of the spectral functions in the SC and CDW phase and afterward, 
we will describe the behaviour of the occurring modes as the system approaches a phase transition.
\newline
The spectral functions corresponding to the individual operators in \eqref{eqn:resolvent_bases} are shown in \autoref{fig:resolvent_overview_SC}.
We chose $U=-2$ for the square lattice and $U=-2.5$ for the simple cubic lattice and $V=\pm0.1$ for both lattices.
\newline
There are a variety of different features. The difference between the two lattices is mostly quantitative in nature.
First and foremost, in the SC phase, there is a sharp peak located at $\omega=0$, only in the phase spectral function,
and another peak, only in the amplitude spectral function, located at $\omega=2\Delta_\text{SC}$.
We identify them with the well-known Leggett and Higgs modes in superconductors.
In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
\newline
The CDW spectral function shows a peak below the continuum only in the SC phase, while having another peak at $\omega=2\Delta$ in the CDW phase.
The AFM spectral function is restricted to the continuum for both phases and both lattices.
For the square lattice, however, there is a peak located at the upper edge of the two-particle continuum.

To further classify the aforementioned peak that lie outside the two-particle continuum,
we turn towards the real part of the Green's function.
We plot it in close proximity to the peaks with a double logarithmic scale and fit the result linearly to obtain.

It is related to the imaginary part by the Kramers-Kronig relations.
